References

### 2015-02-03 cv/CoverLetter/SecondApplicationToKU.tex
Re-arrange documents of career.

I obtained my master's degree in mathematical physics from Lund
University, with a thesis on econophysics supervised by Prof. Sven \AA
berg. Based on the results of the thesis and with some continued work,
Prof. \AA berg and I have written a paper together under the title
``Effect of Heteroscedasticity on the spectrum of an Empirical
Covariance Matrix'' and plan to submit it to {\it Quantitative
  Finance} for publication. In the paper we argued that, on certain
conditions, autocorrelations in the conditional volatilities could
affect the empirical covariance matrixes' spectrum only through the
unconditional distribution of the volatilities. On these
conditions, we derived in the case of small autocorrelations the
spectrum of an empirical covariance matrix. The derivations were based
on results from free probability theory.

>>>>

I obtained my master's degree in mathematical physics from Lund
University, with a thesis on econophysics supervised by Prof. Sven \AA
berg. Based on the results of the thesis and with some continued work,
Prof. \AA berg and I have written a paper together under the title
``Effect of Heteroscedasticity on the spectrum of an Empirical
Covariance Matrix'' and plan to submit it to {\it Quantitative
  Finance} for publication. In the paper we argue that, on certain
conditions, autocorrelations in the conditional volatilities only
affect the empirical covariance matrixes' spectrum through the
unconditional distribution of the volatilities. On these
conditions, we derived in the case of small autocorrelations the
spectrum of an empirical covariance matrix of identical sequences. The
derivations are based on results from free probability theory.
